Storing messages with multipartite neural cliques

### 2014-07-04 Articles/article.tex
modif

	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $1 \le j \le l$ and $1 \le i \le c$, the neuron $j$ in the cluster $i$ is activated if and only if $y_{i,j} = 1$ ; then adding all connections between activated neurons excepting for neurons sharing the same cluster. Thus we obtain a multipartite clique between activated neurons of message.

@@

@@

		\subsubsection{The "$a$ winners take all" rule}
		$a$-rank

@@

		$w = a$

>>>>

	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $1 \le j \le l$ and $1 \le i \le c$, the neuron $j$ in the cluster $i$ is activated if and only if $y_{i,j} = 1$ ; then adding all connections between activated neurons excepting for neurons sharing the same cluster. Thus we obtain a multipartite clique between activated neurons representing a message. The parameter $a$ describing the number of activated neurons per cluster will be called number of activities.

@@

		Retrieving messages occurs by message passing.

@@

		take only maximum score

		\subsubsection{The "$a$ winners take all" rule}

		$a$-rank

@@

		$w = a$	is optimal
